Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-11-01 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd

We reject *H2.2*, finding no evidence that taller trees tend to have traits associated with greater drought resistance. In part because of the large sample size (n=# trees--all individuals of our 12 focal species $\ge$ 10 cm in 25.6 ha), there were very significant (p<0.0001) correlations of $H$ with all species' traits (see Table S5). However, the correlation only matched the predicted direction (*i.e.*, more drought-resistant traits associated to taller trees) in the case of $LMA$, which did not correlate with $R$. Furthermore, although correlations were statistically signifcant, trait variation within each height class overwhelmed any vertical trends (Fig. 2**e-f**).

We support the hypothesis (*H2.3*) that the observed tendency for larger trees to have greater growth reductions during drought (lower $R$) is *not* driven by more drought-sensitive traits in larger trees, but rather by size itself (Tables 1,5). As discussed above, there was little meaningful variation in traits with height at the community level. When $ln[H]$ and hydraulic traits were considered together in multivariate models, the effect of $ln[H]$ on $R$ was consistently negative (Table 5)--reversing a non-signficant positive $ln[H]$-$R$ correlation in the univariate model for the 1999 drought (Table 4).

>>>>

We reject *H2.2*, finding no evidence that taller trees tend to have traits associated with greater drought resistance. In part because of the large sample size (**n=#** trees--all individuals of our 12 focal species $\ge$ 10 cm in 25.6 ha), there were very significant (p<0.0001) correlations of $H$ with all species' traits (see Table S5). However, the correlation only matched the predicted direction (*i.e.*, more drought-resistant traits associated to taller trees) in the cases of $WD$ $LMA$, which were not useful predictors of $R$. Furthermore, although correlations were statistically signifcant, trait variation within each height class overwhelmed any vertical trends (Fig. 2e-f).

We support the hypothesis (*H2.3*) that the observed tendency for larger trees to have greater growth reductions during drought (lower $R$) is driven by height itself, as opposed to more drought-sensitive traits in larger trees (Tables 1,5). As discussed above, there was little meaningful variation in traits with height at the community level. When $ln[H]$ and hydraulic traits were considered together in multivariate models, the effect of $ln[H]$ on $R$ was consistently negative (Table 5)--reversing a non-signficant positive $ln[H]$-$R$ correlation in the univariate model for the 1999 drought (Table 4).
